Estimating contemporary migration rates for iteroparous species using kinship pairs found between populations

### 2022-01-18 latex/ms.tex
add note in Discussion, #14

We presented mainly three novel points in this paper. First, we formulated probabilities of kinship pairs randomly chosen between two populations ($\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$), which provide estimators of the migration number or rate. While similar derivations are found in the context of a mark-recapture method (REF), these are limited to the situation such that sampling can be non-invasive and adult individuals are sampled. Our proposed method can avoid these limitations, where such an advantages is characterized by CKMR method. Second, we revealed that the probabilities of kinship pairs are approximately independent of reproductive potential and thus information about it is not needed for the estimation, if migration event and the potential are independent. This is a useful property of the estimators because heterogeneity of reproductive potential within/between populations are generally observed in iteroprous species. Third, we demonstrated applicability that the estimation can be obtained only from the genetic data (i.e., ${\hat M_5}$ and ${\hat m_4}$). There are several advantages in using the proposed estimator instead of separately estimating $\pi_{\rm HS,bet}$ (and/or $\pi_{\rm PO,bet}$) (via genetic method) and $N_1$ (and/or $N_2$) (via nongenetical method), including simplified sampling and analyzing designs and availability of unified framework of genetic analyzes for detecting PO and HS pairs (similar discussion is found for estimating effective breeding size per census size, $N_{\rm b}/N$, in \cite{Akita_2020}).

@@

Finally, we note several caveats in applying proposed method. Our theory for developing estimators assumes that kinships are detected without any error. There are many algorithms to detect kinship pairs from single nucleotide polymorphisms (SNPs) or short tandem repeats (STRs) (REF), although a HS pair requires many more DNA markers than a PO pair. In addition, iteroprous species potentially has several kinship types such as halfsib-uncle/nephew or halfsib-cousin, which are expected to appear frequently and should be correctly distinguished from HS pairs. It is desirable to estimate in advance how many markers are needed for kinship detections in target populations associated with simulation of a pedigree reconstruction including distant kinships (e.g., \cite{Anderson_2020}).

%必要条件としては、個体数管理のため、細かすぎる時空かんスケールはだめ。大雑把なpopulationを仮定したい時に限る（空間的に細かいグリッドは困難？）、集団構造がspecifyされた後に実施される。繁殖タイミングの間隔の移動を統合したもの、子供の移動については何も言ってない。

>>>>

We presented mainly three novel points in this paper. First, we formulated probabilities of kinship pairs randomly chosen between two populations ($\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$), which provide estimators of the migration number or rate. While similar derivations are found in the context of a mark-recapture method (\RED{REF}), these are limited to the situation such that sampling can be non-invasive and adult individuals are sampled. Our proposed method can avoid these limitations, where such an advantages is characterized by CKMR method. Second, we revealed that the probabilities of kinship pairs are approximately independent of reproductive potential and thus information about it is not needed for the estimation, if migration event and the potential are independent. This is a useful property of the estimators because heterogeneity of reproductive potential within/between populations are generally observed in iteroprous species. Third, we demonstrated applicability that the estimation can be obtained only from the genetic data (i.e., ${\hat M_5}$ and ${\hat m_4}$). There are several advantages in using the proposed estimator instead of separately estimating $\pi_{\rm HS,bet}$ (and/or $\pi_{\rm PO,bet}$) (via genetic method) and $N_1$ (and/or $N_2$) (via nongenetical method), including simplified sampling and analyzing designs and availability of unified framework of genetic analyzes for detecting PO and HS pairs (similar discussion is found for estimating effective breeding size per census size, $N_{\rm b}/N$, in \cite{Akita_2020}).

@@

Finally, we note some caveats in applying proposed method. Our theory for developing estimators assumes that kinships are detected without any error. There are many algorithms to detect kinship pairs from single nucleotide polymorphisms (SNPs) or short tandem repeats (STRs) (\RED{REF}), although a HS pair requires many more DNA markers than a PO pair. In addition, iteroprous species potentially has several kinship types such as halfsib-uncle/nephew or halfsib-cousin, which are expected to appear frequently and should be correctly distinguished from HS pairs. It is desirable to estimate in advance how many markers are needed for kinship detections in target populations associated with simulation of a pedigree reconstruction including distant kinships (e.g., \cite{Anderson_2020}). Our proposed estimators only detect the parental movements on a period between breeding seasons in given populations.

%必要条件としては、個体数管理のため、細かすぎる時空かんスケールはだめ。大雑把なpopulationを仮定したい時に限る（空間的に細かいグリッドは困難？）、集団構造がspecifyされた後に実施される。繁殖タイミングの間隔の移動を統合したもの、子供の移動については何も言ってない。繁殖タイミングの間の移動しか捕捉できない。
